\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{mathptmx}

\geometry { left=25mm, right=25mm, bindingoffset=0mm, top=20mm, bottom=20mm }
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{15pt}
\lhead{Clavianus Juneardo – 2001539682}
\rhead{IN CS RS EN – 1}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
\urlstyle{rm}

\begin{document}

\section*{Questions}
\begin{enumerate}
    \item Jelaskan mengenai profil perusahaan/institusi/komunitas dimana anda ditempatkan!
    \item Jelaskan posisi dan perna anda pada pekerjaan/proyek/bisnis yang sedang dikerjakan!
\end{enumerate}

\section*{Answers}
\begin{enumerate}
    \item Airyrooms (PT Airy Nest Indonesia) is a technology-based Accomodation Network Orchestrator (ANO) which offers hotel and flight reservation with an affordable price. Airyrooms partnered with various best budget hotel in Indonesia that offers hotel management and operation with various type. Under Airyrooms, hotel partner's level of comfort and cleanliness will be standardize to increasing occupancy and revenue. Airyrooms has partnered with more than 1000 hotels that spread throughout Indonesia.
    \item My position as a software engineer intern both back-end and front-end at reservation domain inside core team. My responsibilities are develop, maintain, and improve internal tools that used by team and customer service operational team. 
\end{enumerate}


\end{document}
