\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{mathptmx}

\geometry { left=25mm, right=25mm, bindingoffset=0mm, top=20mm, bottom=20mm }
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{15pt}
\lhead{Clavianus Juneardo – 2001539682}
\rhead{IN CS RS EN – 2}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
\urlstyle{rm}

\begin{document}

\section*{Questions}
\begin{enumerate}
    \item Jelaskan hubungan pekerjaan/proyek/bisnis yang anda kerjakan dengan kompetensi teknis yang anda miliki! (kompetensi teknis adalah kemampuan teknis sesuai dengan bidang ilmu jurusan anda)
    \item Jelaskan teori yang mendukung kompetensi teknis yang dibutuhkan dalam mengerjakan pekerjaan/proyek/bisnis anda!

        (Untuk 4 sks : minimal 2 teori dan 6 referensi. Teori didapat dari referensi textbook, jurnal, makalah ilmiah)

        (Untuk 2 sks : minimal 1 teori dan 3 referensi. Teori didapat dari referensi textbook, jurnal, makalah ilmiah)
    \item Jelaskan hasil pengamatan anda terhadap hubungan antara teori pendukung kompetensi teknis dalam pengerjaan pekerjaan/proyek/bisnis dengan situasi yang anda hadapi di lapangan!
    \item Apa kendala yang anda hadapi dalam pengerjaan proyek/pekerjaan/bisnis terkait kompetensi teknis yang anda miliki?
    \item Apa upaya anda dalam memperdalam/meningkatkan kompetensi teknis untuk menyelesaikan  masalah/mengerjakan proyek/pekerjaan/bisnis anda? (kompetensi teknis adalah kemampuan teknis sesuai dengan bidang ilmu jurusan anda)
\end{enumerate}

\section*{Answers}
\begin{enumerate}
    \item As a technology-based Accomodation Network Orchestrator, my major relate on the technology side of Airyrooms for developing and maintaining web-based internal tools using Java (Dropwizard), React, Redis, PostgreSQL, Docker, Kubernetes and Thymeleaf.
    \item References and theory:
        \begin{enumerate}
            \item Java(Dropwizard): Alexandros Dallas . (2014) . RESTful Web Services with Dropwizard
            \item React: Vipul A M, Prathamesh Sonpatki . (2016) . ReactJS by Example: Building Modern Web Applications with React: Get up and running with ReactJS by developing five cutting-edge and responsive projects
            \item Redis: Tiago Macedo; Fred Oliveira . (2011) . Redis Cookbook [practical techniques for fast data manipulation]
            \item PosstgreSQL: John C. Worsley, Joshua D. Drake, Command Prompt Inc . (2002) . Practical PostgreSQL
            \item Docker: Karl Matthias, Sean P. Kane . (2015) . Docker: Up and Running
            \item Kubernetes: Kelsey Hightower, Brendan Burns, Joe Beda . (2017) . Kubernetes: Up and Running: DIve into the Future of Infrastructure
        \end{enumerate}
    \item The Theory is necessarly needed and very important especially for developer. We need t o know how things work behind the scene to avoid unwanted behavior from a method, to know pros and cons of a method, etc.
    \item Because I work as an enterprise engineer, it is harder to understand the business process than the code itself.
    \item I as a developer write a TIL (Today I Learn) notes for myself to avoid falling on the same hole, writing and reading from technology related articles such as \url{https://dev.to}, or \url{https://medium.com} and doing some self-development to improve myself.
\end{enumerate}


\end{document}
