\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{mathptmx}

\geometry { left=25mm, right=25mm, bindingoffset=0mm, top=20mm, bottom=20mm }
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{15pt}
\lhead{Clavianus Juneardo – 2001539682}
\rhead{EES IN CS RS – 2}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
\urlstyle{rm}

\begin{document}

\section*{Questions}
\begin{enumerate}
    \item Jelaskan hasil pengamatan anda terhadap hubungan antara teori soft skills yang sudah anda jelaskan sebelumnya dengan situasi yang anda hadapi di proyek/pekerjaan/bisnis! 
\end{enumerate}

\section*{Answers}
\begin{enumerate}
    \item My \textbf{self management} skills is challenged when I need to assign a story point on my JIRA task, I need to manage the task and assign a story point cleverly so it won't be   double edged sword for me. 
    \item Even though my team is only consists of 3 people, \textbf{Team Work} is still needed, to avoid a git conflict, or causing a redundant work, also integrating a service with another team is also a team work.
    \item \textbf{Communication} is needed as I said before. Explaining a method that I used to my mentor and coworker on meeting or a technical documentation for example. I need to write and speak clearly, so there's no missing context with my coworkers.
    \item \textbf{Initiative \& Enterprise} is challenged when I need to be proactively research an improvisation. I implement Aspect Oriented Programming on the service by my own will, and it approved by my mentor because it reduce the cost of creating redundant line of code.
    \item \textbf{Problem Solving \& Decision Making} as a developer is a necessary skills. Everytime is a problem solving time. Every step I made must be decide clearly with my team. So we both know the trade-off, pros and cons for every solution that we decide.
    \item As a developer we need to help Product Manager to \textbf{Planning \& Organizing} the next features / tasks. Because both devs and PMs need to know the trade-off, pros, and cons on every decision, devs could help PMs to plan the technical decision while PMs helping on business decision, and at the end of the day we can organize the task effectively.
\end{enumerate}

\end{document}
